\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\title{Rules of the Synixe Gaming Community}

\begin{document}
\maketitle
\newpage

\section{General Operations}
\subsection{Platforms}
\begin{enumerate}
	\item Discord is to be the primary form of text communication.
	\item TeamSpeak 3 is to be the primary form of voice communications.
	\item Discord Roles will be used as the organization's system for designations.
	\item All designations must be also shown in the TeamSpeak server.
\end{enumerate}
\subsection{Servers}
\begin{enumerate}
	\item All dedicated servers used by the community will be hosted by a member of the Executive Board.
	\item The TeamSpeak server IP address shall not be shared until required.
	\item If the TeamSpeak server is unavailable temporary channels shall be created in Discord.
\end{enumerate}
\section{Age}
\paragraph{}
The minimum age required to join is 13. New members between the ages of 13-15 inclusive will be subject to a 3 month probabtion period during which they can be removed if they can not integrate into the community smoothly.
\section{Content} \label{content}
\subsection{Moderators}
\paragraph{}
Moderators are allowed to remove any content they feel is in objective breach of any definitions under Section \ref{content}.
\subsection{Inappropriate Content}
\begin{enumerate}
	\item Any content that is pornographic in nature will be removed.
	\item Any content containing gore, horror, cruelty or violence at the discretion of the Executive Board will be removed.
	\item Any content containing the glorification of illegal activities at the discretion of the Executive Board will be removed.
\end{enumerate}
\subsection{Harassment}
\begin{enumerate}
	\item Targeting an individual because of their race, ethnicity, religon, or sexual orientation will not be tolerated.
	\item Content, symbols, or behaviours of a sexual nature that make the target feel uncomfortable will not be tolerated.
	\item Any harassment at the discretion of the Executive Board will not be tolerated.
	
\end{enumerate}
\section{Cheating \& Exploiting} \label{cheating}
\subsection{Gaming}
\begin{enumerate}
	\item Any deliberate action or attempt to enhance your game play or to give yourself an unfair advantage will not be tolerated.
	\item Any modification of game files or additional modifications outside of what is required by Synixe will not be tolerated.
\end{enumerate}
\subsection{Exploiting}
\begin{enumerate}
	\item Any attempt to gain access to administrative tools will result in an immediate permanent ban.
\end{enumerate}
\section{Dual-Clanning} \label{dual-clan}
\begin{enumerate}
	\item Members of Synixe that hold a position on the Executive Board are asked to refrain from holding a leadership role in other Arma communities. If they wish to hold a leadership position in another community we ask that they resign from their position in Synixe.
	\item All members not on the Executive Board are free to have a leadership role in other communities.
	\item All members are free to participate in the event of other Arma communities.
\end{enumerate}
\section{Conduct} \label{conduct}
\paragraph{}
All members of Synixe are expected to treat their fellow members in a considerate way at all times. Disagreements are fine, hostility is not.
\subsection{Disruptive Behaviour}
\paragraph{}
Disruptive behaviour is any action that degrades the quality of the community for other members at the discrestion of the Executive Board.
\subsection{In Game}
\paragraph{}
We are a casual realism unit. We have no attendance requirements, mandatory training or strict procedures. We do however expect that you take the mission seriously and attempt to complete objectives tactically.
\subsubsection{Team Killing}
\paragraph{}
Intentional Team Killing is not tolerated at any time during any mission.
\subsubsection{Making a Travesty}
\paragraph{}
Making a Travesty of a mission is any action that ruins the enjoyment of the mission for others.
\paragraph{}
Making a Travesty of a mission will result on a kick from the mission on the first occurance and a ban from the mission the second time. If this happens during three seperate missions you will be banned from Synixe.
\section{Mission Making}
\subsection{Sanctioned Events}
\paragraph{}
All missions used in sanctioned events must meet one of the folling criteria.
\begin{itemize}
  \item Made by a MissionMaker in Synixe that has passed automated checks
  \item Made by a MakerInTraing after a review by a MissionMaker and approved by a member of the Executive Board that is also a MissionMaker
  \item Not made a member of Synixe, that has been reviewed, tested, and approved by a Manager
\end{itemize}.
\subsection{MissionMaker}
\paragraph{}
A mission maker is anyone that has completed the MakerInTraining process. MissionMakers have the ability to upload missions to the Synixe Dashboard to undergo an automated review.
\subsection{MakerInTraining}
\paragraph{}
Any member may become a MakerInTraining after participating in at least 3 sanctioned events.
\paragraph{}
They will be given access to the mission making resources and MissionMakers will help them learn how Synixe makes our missions
\subsubsection{Mission}
Once the Executive Board feel a MakerInTraining is ready to host a sanctioned event they can create a mission. It must be reviewed by atleast one MissionMaker and approved by a member of the Executive Board that is a MissionMaker before being hosted. At least 2 members of the Executive Board must be present at the event.
\subsubsection{Succession to MissionMaker}
After hosting a mission, a majority vote is required in a meeting of the Executive Board on whether the MakerInTraining will join the mission making team. If denied, they will remain in training and do another mission. If accepted, the Executive Board will announce the succession.
\section{Names} \label{names}
\begin{enumerate}
	\item Names can not be offensive in any way and are subject to all rules under Section \ref{content}.
	\item Names should be clear and easy to read.
	\item Names can not exceed 4 syllables.
	\item Names should be easily pronouncable so people can easily address you on voice comms.
	\item Names must be unique within Synixe.
	\item Names must be consistent across all platforms. This helps people learn who is who.
	\item Names should include an obvious 1 or 2 syllable shorter name within them.
	\item Names must not include ranks.
	\item Names must not include phrases or words that could be misinterpreted during gameplay.
\end{enumerate}
\section{Reporting}
\paragraph{}
If you know about anyone breaking a rule found in Sections \ref{content}, \ref{cheating}, \ref{dual-clan}, \ref{conduct}, or \ref{names} please report it to a member of the Executive Board (Managers and Moderators) of Synixe in a direct message or by using the ?anon command in a direct message with the Synixe Bot. Any reports given this way will remain annonymous.
\end{document}